### 2016-09-21 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to burner report

\subsubsection{First Floor of Both Structures}
The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft). The joints and gaps between the blocks were filled with high temperature insulation.

@@

All first floor exterior doors were made of steel. The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track. Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by a stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior side of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

\subsubsection{Leakage}
An air leakage measurement system was used to measure the amount of leakage associated with each structure. The amount of leakage in the East Structure was measured as 0.024~m$^2$. For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) during Tests~24 and 25.

@@

% \subsubsection{Dimensions}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

>>>>

\subsubsection{First Floor of Both Structures}
The first floor of each structure had outer walls composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft). The joints and gaps between the blocks were filled with high temperature insulation. All doors along the outer walls were composed of steel.

@@

The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track. Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick cement board.
\FloatBarrier

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by an interior stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior side of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

\subsubsection{Leakage}
An air leakage measurement system was used to measure the amount of leakage associated with each structure. The amount of leakage in the East Structure was measured as 0.024~m$^2$. For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was fully closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) used Tests~24 and 25.
\clearpage

@@

Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
